%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineering Manager - Applied AI} % Job title
    {Temus (Temasek backed Digital Transformation Company)} % Organization
    {Singapore} % Location
    {Sep. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {Reduced financial due diligence time by 20\% and costs by 37\% by leading development of an AI financial assistant that combined LLMs with RAG and SQL AST parsing, achieving 70\% accuracy through on-premise deployment of the SQLCoder Text-to-SQL model.}
        % \item{Improved Thai language intent detection accuracy by 54\% by architecting a multilingual ASR system utilizing fine-tuned Whisper, Voice Activity Detection, and Speaker Diarization with Llama-based transcript correction.}
        % \item{Reduced sales representative onboarding time by 20\% across 1,000+ users by leading development of DialogForge, a real-time voice-to-voice training platform combining Whisper, Llama3, Elevenlabs, and Unreal Engine Metahuman.}
        % \item{Decreased LLM serving costs by 40\% by architecting LinguaForge, a multi-cloud platform utilizing Kubernetes, SkyPilot, and vLLM with S-LoRA orchestration for optimized adapter management.}
        % \item{Add point for architecture and design}
        % \item {Scaled engineering team from 3 to 25 developers across 3 squads by implementing agile methodologies, mentoring programs, and technical development paths, resulting in 40\% faster project delivery and 30\% improvement in code quality metrics.}
        \item{Led AI implementations across insurance, finance, and government sectors, driving enterprise digital transformation solutions that generated S\$12M in annual revenue and winning 7/8 competitive deals through exceptional POC delivery.}
        \item{Led AI Investment Analyst Assistant delivery, integrating advanced NLP, knowledge retrieval, and database querying capabilities that reduced due diligence time by 20\% and costs by 37\%. Achieved 70\% accuracy in 4 months (2 months ahead of schedule), driving \$10M+ in new projects with 77\% client satisfaction.}
        \item{Reduced LLM serving costs 40\% and POC development time 80\% by architecting multi-cloud platform with Kubernetes, vLLM and S-LoRA orchestration. Designed modular infrastructure that became company standard, enabling 3x faster model iterations across 5 product lines.}
        \item{Led DialogForge development—a voice-to-voice sales representative training platform using Whisper, Llama3, and Metahuman—reducing onboarding time by 20\% for 1,000+ users while improving training outcomes by 30\%.}
        \item{Advanced implementation of knowledge injection in Llama3 8B models, reducing hallucinations by 95\% and improving task accuracy by 50\%. Pioneered representation engineering in Mistral/Llama models for production-grade personality control.}
        \item{Saved \$500K annually by cutting service center call volume 40\% through a custom Thai language processing system. Delivered 54\% higher intent detection accuracy using fine-tuned Whisper ASR, voice activity detection, and speaker diarization.}
        \item{Scaled engineering 8x (3→25 developers) and cut delivery time 40\% by implementing agile methods and structured mentorship. Established LLM standards improving code quality 30\%, adopted by 4 business units with \$1M efficiency savings.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer, NLP} % Job title
    {Aaqua (Stealth Social Media Startup)} % Organization
    {Singapore} % Location
    {Jun. 2021  - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reduced manual content moderation effort by 30\% and maintained 85\% recall across image perturbations by implementing a CLIP model-based system with robustness to rotation, scaling, cropping and chroma-noise for detecting policy-violating content.}
        \item {Improved spam detection recall to 78\% from baseline 45\% by developing an ML filtering system using Microsoft MiniLM, FastAPI, and Sagemaker trained on open SMS datasets, processing 1M+ messages daily.}
        \item {Decreased business report turnaround time by 10\% and reduced analytics request backlog by 40\% by architecting an ETL platform combining Airflow orchestration, Datahub data management, and dashboards via Superset.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer, NLP} % Job title
    {Radicali (Regulatory Compliance Startup)} % Organization
    {Singapore} % Location
    {Oct. 2019 - May. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Secured \$1M funding by developing a regulation-policy matching system that identified non-compliant clauses and their monetary impact with 65\% accuracy, using documents-as-graphs architecture with GPT-2 and knowledge distillation to acheive 20x faster inference.}
        \item{Increased web scraping success rates by 45\% and reduced infrastructure costs by 25\% by implementing a serverless solution using Scrapy with AWS Lambda and Fargate integration.}
        \item{Delivered successful product-market fit for 3 major clients representing \$500K ARR by managing a 15-person development team, establishing technical delivery processes, and implementing regular stakeholder feedback loops.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Scripbox (FinTech Startup)} % Organization
    {Bangalore, India} % Location
    {Oct. 2016 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Increased company revenue by 10\% and achieved 93\% prediction accuracy by developing customer lifetime value models using Hierarchical Bayesian methods, enabling targeted retention strategies for highest-value segments.}
        \item{Improved customer experience and portfolio transparency for \$3M AUM by implementing a portfolio management platform in Elixir that delivered 10x performance improvement, displaying real-time investment returns and metrics.}
        \item{Reduced customer onboarding time by 50\% and decreased document processing errors by 35\% by architecting an automated pipeline combining YOLOv2 object detection with Tesseract OCR for identity and financial document verification.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Engineer} % Job title
    {Zopper (Ecommerce Startup)} % Organization
    {Bangalore, India} % Location
    {Jan. 2016 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved order processing efficiency by 13\% and reduced system downtime by 40\% by implementing a LinkedIn Databus-based database migration system that enabled zero-downtime schema changes across the e-commerce platform.}
        \item {Increased retail sales by 20\% and expanded product catalog by 35,000 SKUs by developing a catalog extension platform that enabled national distributor product sourcing and real-time inventory synchronization.}
      \end{cvitems}
    }
\end{cventries}
