%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected Projects}

\hypersetup{%
  linkbordercolor=red,% hyperlink borders will be red
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {\href{https://bit.ly/exstan-elixirconf}{bit.ly/exstan-elixirconf}}
    {ExStan: Elixir <> Stan for Probabilistic Modeling} % Event
    {Lisbon, Portugal} % Location
    {Apr. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Presented a talk on \href{https://github.com/goodhamgupta/ex_stan}{Probabilistic Programming using ExStan, Stan SDK in Elixir} at ElixirConfEU 2024 }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://bit.ly/mlsg-ssm}{bit.ly/mlsg-ssm}}
    {State Space Models for Language Modeling} % Event
    {Singapore} % Location
    {Feb. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Presented State Space Models (SSMs), an alternative architecture for Language Modelling, in the ML Singapore Meetup }
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {\href{https://bit.ly/on-device-llm-healthcare}{bit.ly/on-device-llm-healthcare}}
    {AI Driven Patient Engagement in Healthcare} % Event
    {Singapore} % Location
    {Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Engineered mobile app with optimized on-device LLM (~3B params) and confidence-based cloud fallback, using token logits, to large model running on the cloud}
        \item {Successfully piloted with 100 users, enabling accessible medical guidance in low-resource regions}
      \end{cvitems}
    }
%---------------------------------------------------------


%---------------------------------------------------------
  \cventry
    {\href{https://bit.ly/attention-image-captioning}{bit.ly/attention}}
    {End-to-End Attention based Image Captioning} % Event
    {Singapore} % Location
    {Apr. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented as part of a course project at NUS, and finished in top 10\% of the leaderboard in the Kaggle contest. }
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {\href{https://bit.ly/attention-image-captioning}{https://bit.ly/hierachical-clv}}
    {Hierarchical Bayesian CLV Model } % Event
    {Moscow, Russia} % Location
    {Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed and presented at DeepBayes2019, a novel Bayesian hierarchical model for CLV prediction that integrates customer demographics, achieving 37\% improvement in valuation accuracy and enabling data-driven marketing strategies }
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/goodhamgupta}{GitHub}, \href{https://bit.ly/elixir-packages}{Elixir Packages}}
    {Open-Source Contributor} % Event
    {Singapore} % Location
    {Aug. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Open source contributor to Nx, OpenMined and Snowplow Analytics. Packages have over \textbf{250k} downloads}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
